\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{longtable}
\geometry{margin=1in}

\title{Software Requirements Specification (SRS) \\ \large Amber Molecular Dynamics Web Interface}
\author{Group number 7}
\date{\today}

\begin{document}

\maketitle

\tableofcontents
\newpage

%---------------------------------------
\section*{Version Description}
\addcontentsline{toc}{section}{Version Description}

\begin{longtable}{|m{2.5cm}|m{9cm}|m{3cm}|}
\hline
\textbf{Version} & \textbf{Description} & \textbf{Date Added} \\ \hline
1.0 & SRS for Snapshot 1 that helps defining requirements for the Amber MD web interface. & \today \\ \hline
\end{longtable}

%---------------------------------------
\section{Introduction}
\subsection{Purpose}
The purpose of this Software Requirements Specification (SRS) is to
define the functional and non-functional requirements of the
\textbf{Amber Molecular Dynamics Web Interface}. The system
aims to make it easier for users to configure, run, and monitor Amber
molecular dynamics simulations without manually dealing with all
command-line options.

\subsection{Intended Audience}
This document is intended for:
\begin{itemize}
    \item Developers implementing the system.
    \item Testers verifying that requirements are met.
    \item Researchers who will use the system to run Amber MD simulations.
\end{itemize}

\subsection{Overview of the Software}
The Amber Molecular Dynamics Web Interface is a web application that:
\begin{itemize}
    \item Provides forms and wizards for configuring Amber simulations.
    \item Submits jobs to an Amber installation on the server or cluster.
    \item Tracks job status and notifies users upon completion.
    \item Allows users to download key output files.
\end{itemize}

%---------------------------------------
\section{External Interface Requirements}
\subsection{User Interface}
The user interface must:
\begin{itemize}
    \item Allow users to register, log in, and log out.
    \item Provide a dashboard listing all simulations and their statuses.
    \item Provide a ``New Simulation" page with fields for:
          structure file, force field, simulation length, temperature,
          and other key parameters.
    \item Show job status like Pending, Running, Completed, or Failed.
    \item Provide links or buttons to download result files.
\end{itemize}

\subsection{Software Interfaces}
The system will interact with:
\begin{itemize}
    \item \textbf{Amber MD Software}: Executable commands
          on the server. The backend will generate proper input files and
          invoke these commands.
    \item \textbf{Operating System}: For launching processes and accessing
          the file system.
    \item \textbf{Database Management System}: For storing users, simulations,
          jobs, and file references.
\end{itemize}

%---------------------------------------
\section{Legal and Ethical Considerations}
\subsection{Data Storage and Privacy}
\begin{itemize}
    \item The system will store user accounts that have info like username, email, password hash.
    \item Passwords must never be stored in plain text.
    \item Simulation data may be sensitive research data
          and must be accessible only to the owner.
\end{itemize}

\subsection{Legal and Ethical Issues}
\begin{itemize}
    \item The system must respect the Amber licensing terms and only run
          on properly licensed installations.
    \item Users should be informed that they are responsible for any
          data they upload.
    \item The system must not share simulation data with third parties
          without user consent.
\end{itemize}

%---------------------------------------
\section{Glossary}
\begin{longtable}{|m{4cm}|m{10cm}|}
\hline
\textbf{Acronym} & \textbf{Definition} \\ \hline
Amber & Suite of biomolecular simulation programs for molecular dynamics \\ \hline
MD & Molecular Dynamics \\ \hline
UI & User Interface \\ \hline
API & Application Programming Interface \\ \hline
PDB & Protein Data Bank file format \\ \hline
\end{longtable}

\end{document}
