\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{array}
\geometry{margin=1in}

\title{Software Requirements Specification (SRS) \\ \large Amber Molecular Dynamics Web Interface}
\author{Group number 7}
\date{\today}

\begin{document}

\maketitle

\tableofcontents
\newpage

%---------------------------------------
\section*{Version Description}
\addcontentsline{toc}{section}{Version Description}

\begin{longtable}{|m{2.5cm}|m{9cm}|m{3cm}|}
\hline
\textbf{Version} & \textbf{Description} & \textbf{Date Added} \\ \hline

1.0 & Initial SRS draft defining purpose, audience, and system overview. & \today \\ \hline

1.1 & Added External Interface Requirements section (UI requirements, software interfaces). & \today \\ \hline

1.2 & Added Legal and Ethical Considerations section (data privacy, license rules). & \today \\ \hline

\end{longtable}




%---------------------------------------
\section{Introduction}
\subsection{Purpose}
The purpose of this Software Requirements Specification (SRS) is to
define the functional and non-functional requirements of the
\textbf{Amber Molecular Dynamics Web Interface}. The system
aims to make it easier for users to configure, run, and monitor Amber
molecular dynamics simulations without manually dealing with command-line interfaces.

\subsection{Intended Audience}
This document is intended for:
\begin{itemize}
    \item Developers implementing the system.
    \item Testers verifying that requirements are met.
    \item Researchers who will use the system to run Amber MD simulations.
\end{itemize}

\subsection{Overview of the Software}
The Amber Molecular Dynamics Web Interface is a web application that:
\begin{itemize}
    \item Provides forms and wizards for configuring Amber simulations.
    \item Submits jobs to an Amber installation on the server or compute cluster.
    \item Tracks job status and notifies users upon completion.
    \item Allows users to download key output files.
\end{itemize}

%---------------------------------------
\section{External Interface Requirements}
\subsection{User Interface}
The user interface must:
\begin{itemize}
    \item Allow users to register, log in, and log out.
    \item Provide a dashboard listing simulations and statuses.
    \item Provide a ``New Simulation" page with fields for structure file,
          force field, simulation length, temperature, and other parameters.
    \item Show job statuses: Pending, Running, Completed, Failed.
    \item Provide links/buttons to download result files.
\end{itemize}

\subsection{Software Interfaces}
The system will interact with:
\begin{itemize}
    \item \textbf{Amber MD Software}: Executable Amber commands on server-side.
    \item \textbf{Operating System}: For launching processes and reading/writing files.
    \item \textbf{Database Management System}: For storing users, simulations, jobs, files.
\end{itemize}

%---------------------------------------
\section{Legal and Ethical Considerations}
\subsection{Data Storage and Privacy}
\begin{itemize}
    \item The system will store user accounts including username, email, and password hash.
    \item Passwords must never be stored in plain text.
    \item Simulation data may represent sensitive research and must be kept private.
\end{itemize}

\subsection{Legal and Ethical Issues}
\begin{itemize}
    \item The system must comply with Amber license requirements.
    \item Users are responsible for ensuring they own rights to uploaded data.
    \item No simulation data may be shared without explicit consent.
\end{itemize}

%---------------------------------------
\section{Non-Functional Requirements}

\subsection{Performance Requirements}
\begin{itemize}
    \item The system must update job status at least every 30 seconds.
    \item Input file generation for a simulation setup must complete within 2 seconds.
\end{itemize}

\subsection{Security Requirements}
\begin{itemize}
    \item All passwords must be hashed using a secure algorithm.
    \item Users may only access their own simulations and files.
\end{itemize}

\subsection{Usability Requirements}
\begin{itemize}
    \item A new simulation setup workflow must be completable in under 5 minutes.
    \item UI forms must validate required fields before submission.
\end{itemize}

\subsection{Reliability Requirements}
\begin{itemize}
    \item System must maintain simulation metadata even if the backend restarts.
\end{itemize}

\subsection{System Constraints}
\begin{itemize}
    \item Requires a valid licensed installation of Amber.
    \item Job execution depends on available CPU/GPU compute resources.
\end{itemize}

%---------------------------------------
\section{Glossary}
\begin{longtable}{|m{4cm}|m{10cm}|}
\hline
\textbf{Acronym} & \textbf{Definition} \\ \hline
Amber & Suite of biomolecular simulation tools \\ \hline
MD & Molecular Dynamics \\ \hline
UI & User Interface \\ \hline
API & Application Programming Interface \\ \hline
PDB & Protein Data Bank file format \\ \hline
\end{longtable}

\end{document}
