\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{longtable}
\geometry{margin=1in}

\title{User Manual \\ \large Amber Molecular Dynamics Web Interface}
\author{Group Number 7}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

%---------------------------------------
\section{Introduction}

This User Manual provides step-by-step instructions for using the Amber Molecular Dynamics
Web Interface. It assists researchers in submitting simulations, monitoring job progress,
and downloading simulation output files.

%---------------------------------------
\section{Getting Started}

\subsection{Accessing the System}
Users access the system via a web browser, but in order to access features they will need to create an account.

\subsection{Creating an Account}
\begin{enumerate}
    \item Navigate to the Login Page.
    \item Click “Create Account.”
    \item Enter username, email, and password.
\end{enumerate}

\subsection{Logging In}
\begin{enumerate}
    \item Enter your username and password.
    \item Click “Login.”
\end{enumerate}

%---------------------------------------
\section{Running a Simulation}

\subsection{Step 1: Open the New Simulation Page}
Click “New Simulation” on the dashboard.

\subsection{Step 2: Upload Files}
Upload:
\begin{itemize}
    \item Structure file (PDB/mol2)
    \item Force field parameters (optional)
\end{itemize}

\subsection{Step 3: Enter Simulation Parameters}
Fill in:
\begin{itemize}
    \item Force field
    \item Temperature
    \item Simulation length
    \item Time step
    \item Minimization/equilibration settings
\end{itemize}

\subsection{Step 4: Submit Simulation}
Click “Submit.”  
A simulation entry will appear in your dashboard.

%---------------------------------------
\section{Monitoring Job Status}

Simulation statuses:
\begin{itemize}
    \item \textbf{Pending} – Waiting to run
    \item \textbf{Running} – Amber execution in progress
    \item \textbf{Completed} – Finished successfully
    \item \textbf{Failed} – Error occurred
\end{itemize}

Click “View Details” to:
\begin{itemize}
    \item Read live log output
    \item View timestamps
    \item Inspect progress indicators
\end{itemize}

%---------------------------------------
\section{Downloading Results}

Once a job completes:
\begin{enumerate}
    \item Go to Dashboard
    \item Click “Download Outputs”
\end{enumerate}

Available downloads:
\begin{itemize}
    \item Trajectory file (.mdcrd)
    \item Topology file (.prmtop)
    \item Energy log
    \item Restart file
\end{itemize}

%---------------------------------------
\section{Troubleshooting}

\begin{itemize}
    \item \textbf{Simulation failed}: Check input file formats and parameters.
    \item \textbf{No output files}: Verify job completed successfully.
    \item \textbf{Cannot log in}: Reset password using “Forgot Password.”
\end{itemize}

%---------------------------------------
\section{Contact}
For assistance, contact the project maintainers.

\end{document}
